### 2019-06-21 TFM.tex
Demo acabada

\begin{definition}
	A (hyper)graph $G$ is $i,j,r$-rich for some $i,j,r\in \N$, if for any rooted tree $T$
	of radius at most $r$ there are $x_1,\dots,x_i\in V(G)$ such that
	\begin{itemize}
		\item The $N(x_l;r)$'s are disjoint.
		\item The $N(x_l;r)$'s do not intersect $Core(G,r)$
		\item $N(x_l;r)(x_l) \morph{j} T$.		
	\end{itemize} 
\end{definition}

@@

>>>>

\begin{definition}
	A (hyper)graph $G$ is $j,r$-rich for some $j,r\in \N$, if for any rooted tree $T$
	of radius at most $r$ there are $x_1,\dots,x_j\in V(G)$ such that
	\begin{itemize}
		\item The $N(x_l;r)$'s are disjoint.
		\item The $N(x_l;r)$'s do not intersect $Core(G,r)$
		\item $N(x_l;r)(x_l) \morph{j} T$.		
	\end{itemize} 
\end{definition}

@@

\begin{lemma} 
	Let $(T_1,x)$ and $(T_2,y)$ be rooted trees such that for some $k>0$ 
	$T_1 \morph{k} T_2$. Then, for any $0\leq j < k$, it is satisfied
	$T_1 \morph{j} T_2$.
\end{lemma}
\begin{proof}
	Fix $j<k$. The proof is by induction on the radius of $T_1$ and $T_2$.
	\begin{itemize}
		\item If they have radius at most $0$ they are $j$-morphic by definition. 
		\item Suppose now that they have radii at most $r$. Let $e_1$ be an edge with root
		$x$ in $T_1$ and $e_2$ be an edge of root $y$ in $T_2$ such that $e_1 \morph{k} e_2$.
		Then $e_1=[x_1,\dots,x_a]$ and $e_2=[y_1,\dots,y_a]$ for some vertices such that for all
		$i=1,\dots, a$ either 
		\begin{itemize}
			\item $Tree(x_i)\morph{k} Tree(y_i)$, and because of the induction hypothesis 
			$Tree(x_i)\morph{j} Tree(y_i)$. 
			\item Or $x_i=x$ and $y_i=y$.
		\end{itemize}
		In consequence $e_1\morph{j} e_2$. Then, any class $C$ 
		of $j$-morphic edges in trees of radius at most
		$r$ is union of classes $D_1,\dots, D_s$ of $k$-morphic edges in 
		trees of radius at most $r$. Then
		\[(T_1,C)=\sum_{i=1}^s (T_1, D_i) \text{, and }	(T_2,C)=\sum_{i=1}^s (T_2, D_i).\]	
	 	Both of the above sums coincide if all the $(T_1, D_i)$'s are not greater than $k$ or
	 	both are greater than $k$ otherwise. As $j\leq k$ this implies
	 	\[\text{Either }(T_1,C)=(T_2,C) \text{ or } (T_1,C),(T_2,C)\geq j+1 ,\]
	 	and $T_1\morph{j}T_2$. 		
	\end{itemize}
\end{proof}

\begin{corollary}
	Let $G_1(c_1,\dots, c_t)$, and $G_2(c_1,\dots,c_t)$ be graphs
	with constants such that $G_1(c_1,\dots, c_t)\morph{k}G_2(c_1,\dots,c_t)$.
	Then, for any $j<k$, $G_1(c_1,\dots, c_t)\morph{j}G_2(c_1,\dots,c_t)$.
\end{corollary}

\begin{lemma}
	Let $(T_1,x)$ and $(T_2,y)$ be rooted trees such that for some $k>0$ 
	$T_1 \morph{k} T_2$. Then, for any $r\geq 0$, $N(x;r)\morph{k} N(y;r)$.
\end{lemma}
\begin{proof}
	The proof is by induction on the radius of $T_1$ and $T_2$.
	\begin{itemize}
		\item If they have at most radius $0$ the statement is vacuously true. 
		\item Suppose now that they have radii at most $r$. Let $e_1$ be an edge with root
		$x$ in $N(x;r)$ and $e_2$ be an edge of root $y$ in $N(y;r)$ such that $e_1 \morph{k} e_2$
		when both edges are considered in $T_1$ and $T_2$ respectively. We want to prove that
		$e_1 \morph{k} e_2$ as well when they are considered as edges in $N(x;r)$ and $N(y;r)$.
		By definition we can write $e_1=[x_1,\dots,x_a]$ and 
		$e_2=[y_1,\dots,y_a]$ for some vertices such that for all
		$i=1,\dots, a$ either 
		\begin{itemize}
			\item $Tree(x_i)\morph{k} Tree(y_i)$, and because of the induction hypothesis 
			\[Tree(x_i)\cap N(x_i;r-a) \morph{k} Tree(y_i)\cap N(y_i;r-a).\] 
			\item Or $x_i=x$ and $y_i=y$.
		\end{itemize}
		In consequence $e_1 \morph{k} e_2$ as edges in $N(x;r)$ and $N(y;r)$. 
		This implies that for any $k$-morphism class of rooted edges $C$ of trees with
		radii less than $r$ there are $k$-morphism classes $D_1,\dots,D_c$ of rooted edges
		of trees with radii at most $r$ such that
		\[ (N(x;r),C) = (T_1, D_1)\cup \dots \cup (T_1,D_a), \]
		and 
		\[(N(y;r),C) = (T_2, D_1)\cup \dots \cup (T_2,D_a).\]
		And we can easily obtain that either
		$|(N(x;r),C)|=|(N(y;r),C)|$ or $|(N(x;r),C)|,$ $
		|(N(y;r),C)|\geq k+1$. 	Thus $N(x;r)\morph{k} N(y;r)$.
	\end{itemize}	
\end{proof}

\begin{lemma}
	Let $(T_1,x),(T^\prime_1,x), (T_2, y)$ and $(T^\prime_2,x)$ 
	be rooted trees satisfying $T_1\morph{k} T_2$.
	$T_1^\prime\morph{k} T_2^\prime$ for some 
	$k\geq 0$ and $V(T_1)\cap V(T_1^\prime)=x$, 
	$V(T_2)\cap V(T_2^\prime)=y$. Then
	$T_1\cup T_1^\prime \morph{k} T_2\cup T_2^\prime$.
\end{lemma}
\begin{proof}
	Let $C$ be a $k$-morphism class of rooted edges. Then
	\[|(T_1\cup T_1^\prime,C)|= |(T_1,C)|+ |(T_1^\prime,C)|, \text{and }\]
	\[|(T_2\cup T_1^\prime,C)|= |(T_2,C)|+ |(T_2^\prime,C)|.\]
	And it follows easily that either
	\[|(T_1\cup T_1^\prime,C)|=|(T_2\cup T_2^\prime,C)|,\]
	or both quantities are greater than $k$. 
\end{proof}

\begin{lemma} 
	Let $(T_1,x)$, $(T_2, y)$ be rooted trees and let 
	$(T^\prime_1,x)$ and $(T^\prime_2,y)$ be sub-trees of 
	$T_1$ and $T_2$ respectively. Let $k\geq 0$.
	If there is an isomorphism 
	$f:T^\prime_1 \rightarrow T^\prime_2$ such that $f(x)=y$ and
	for all $x_1\in V(T^\prime_1)$
	\[ Tree(x_1,T^\prime_1)\morph{k} Tree(f(x_1),T^\prime_2),\]
	then $T_1\morph{k}T_2$. 
\end{lemma}
\begin{proof}
	The proof is, again, by induction on the radius of $T^\prime_1$ and $T^\prime_2$.
	\begin{itemize}
		\item If $T^\prime_1$ and $T^\prime_2$ have radius zero, then they consist only of
		$x$ and $y$ respectively. 
		\item Suppose that $T^\prime_1$ and $T^\prime_2$ have at most $r$. Let $x_1\neq x$ be
		a vertex in an edge $e$ rooted at $x$ such that $e\in T^\prime_1$.
		Then $Tree(x_1, T_1)$ and $Tree(x_1,T^\prime_1)$ satisfy the hypothesis of the lemma,
		and the radius of $Tree(x_1,T^\prime_1)$ is strictly less than $r$. Then by the induction
		hypothesis $Tree(x_1, T_1)\morph{k} Tree(f(x_1),T_2)$. In consequence $e\morph{k}f(e)$
		and using the previous lemma successively we get $T_1\morph{k} T_2$.
	\end{itemize}
\end{proof}

\begin{theorem}
	Let $G_1(c_1,\dots, c_t)$, and $G_2(c_1,\dots,c_t)$ be graphs
	with constants such that for some $r\in N$
	\[ Core(G_1(c_1,\dots, c_t);r)\morph{k} Core(G_2(c_1,\dots,c_t);r)\]
	through $f$. 
	Then, for any $s<r$
	\[ Core(G_1(c_1,\dots, c_t);s)\morph{k} Core(G_2(c_1,\dots,c_t);s).\]
\end{theorem}
\begin{proof}
	Fix $s<r$. Let us introduce some notation
	\[ H_i:= Core(G_i(c_1,\dots, c_t);r) \quad \text{for }i=1,2.\]
	\[ H^\prime_i:= Core(G_i(c_1,\dots, c_t);s) \quad \text{for }i=1,2.\]
	One can check $H^\prime_i\subseteq H_i$ for $i=1,2$, and that the isomorphism 
	$f:Center(H_1)\rightarrow Center(H_2)$ restricts to one between
	$Center(H^\prime_1)$ and $Center(H^\prime_2)$. Let $v\in Center(H^\prime_1)$.
	Let $T=Tree(v,H^\prime_1)\cap Center(H_1)$. It is not hard to see that $T$ is connected 
	and in consequence is a tree. The following identity holds:
	\[ Tree(v,H^\prime_1)= (Tree(v,H_1)\cap N(v;s)) \cup Tree(T,H^\prime_1) \]
	Also, for any $w\in V(T)$
	\[Tree(w,Tree(v,H^\prime_1),T) = Tree(w,H_1)\cap N(w; s-dist(Center(H^\prime_1),w)).\]
	So, by lemma REF 
	\[Tree(w,Tree(v,H^\prime_1),T)\morph{k}Tree(f(w),Tree(f(v),H^\prime_2),f(T)).\]
	In consequence, by lemma REF,
	\[Tree(T,H^\prime_1)\morph{k} Tree(f(T),H^\prime_2).\]
	Using that 
	\[Tree(v,H_1)\cap N(v;s)\morph{k} \morph{k} Tree(v,H_1)\cap N(v;s),\]
	and lemma REF we obtain
	\[Tree(v,H^\prime_1)\morph{k} Tree(f(v),H^\prime_2) .\]
	Hence, $H^\prime_1\morph{k} H^\prime_2$, as desired. 
\end{proof}

\begin{lemma}
	Let $(T_1,x)$, $(T_2, y)$ be rooted trees such that for some $k\geq 0$
	$T_1\morph{k} T_2$. Let $e_1$ and $e_2$ be initial edges of $T_1$ and $T_2$
	such that $e_1\morph{k} e_2$. Then $T_1\setminus e_1\morph{k-1} T_2\setminus e_2$.
\end{lemma}

\begin{proof}
	For any $k$-morphism class $C$ of rooted edges clearly either
	\[|(T_1\setminus e_1,C)|=|(T_2\setminus e_2,C)|,\]
	or both quantities are greater than $k-1$.
	Now, using that any $k-1$ morphism class of rooted edges is union of
	$k$ morphism classes the result follows. 	
\end{proof}

\begin{lemma}
	Let $(T_1,x_1)$, $(T_2,x_2)$ be rooted trees such that for some $k\geq 0$
	$T_1\morph{k} T_2$. For $i=1,2$, given a vertex $v\in V(T_i)$ let us denote by
	$P(v)$ the unique path between $v$ and $x_i$.
	Then for any $v\in V(T_1)$ there is a vertex $w\in V(T_2)$ and an isomorphism
	$f:P(v)\rightarrow P(w)$ such that
	\begin{itemize}
		\item[(1)]  $f(x_1)=x_2$ and $f(v)=w$.
		\item[(2)] For any edge $e\in E(P(v))$, $e\morph{k} f(e)$.
		\item[(3)] For any vertex $y\in V(P(v))$, $Tree(y,T_1)\morph{k} Tree(f(y),T_2)$.
	\end{itemize}
\end{lemma}
\begin{proof}
	The proof is by induction on $d(x_1, v)$.
	\begin{itemize}
		\item If $d(x_1,v)=0$ then $x_1=v$ and the statement is true taking $w=x_2$.
		\item Suppose now that $d(x_1,v)=r$. Then one can write the path $P(v)$ as a
		succession of edges $e_1,e_2,\dots, e_s$, where $v\in e_s$. Let $v^\prime$ be 
		the root of $e_s$. Then $d(x_1,v^\prime)=r-a(e_s)+1$. Thus, by the
		induction hypothesis there exists $w^\prime$ such that there is an isomorphism
		$f: P(v^\prime)\rightarrow P(w^\prime)$ with the required properties. 
		In particular, $Tree(v^\prime,T_1)\morph{k}Tree(w^\prime,T_2)$, so there is an
		edge $e^\prime$ rooted at $w^\prime$ with the same $k$-type as $e_s$. Then one can write
		\[e_s=[v_1,\dots,v_a], \quad  e^\prime=[w_1,\dots,w_a], \]
		in a such a way that for some $i$, $v_i=v^\prime$ and $w_i=w^\prime$ and for all $j\neq i$
		$Tree(v_j,T_1)\morph{k} Tree(w_j,T_2)$. Let $j$ be such that $v=v_j$. Then we can take
		$w=w_j$, and extend the isomorphism $f$ in the evident way. 
	\end{itemize}
\end{proof}

\begin{theorem} 
	Let $G_1(c_1,\dots, c_t)$, and $G_2(c_1,\dots,c_t)$ be graphs
	with constants such that 
	\[ Core(G_1(c_1,\dots, c_t);r)\morph{k} Core(G_2(c_1,\dots,c_t);r)\]
	by means of $f$. 
	Then, for any vertex $x\in Core(G_1(c_1,\dots, c_t);r)$ there is a vertex
	$y\in Core(G_2(c_1,\dots, c_t);r)$ such that 
	\[Core(G_1(c_1,\dots, c_t,c_{t+1}[v_1]);r)\morph{k-1} Core(G_2(c_1,\dots,c_t,c_{t+1}[v_2]);r)\]
\end{theorem}
\begin{proof}
	Let us introduce some notation:
	\[H_i:=Core(G_i(c_1,\dots, c_t);r)\quad \text{for }i=1,2. \]
	\[H^\prime_1:=Core(G_1(c_1,\dots, c_t,c_{t+1}[v_1]);r).\]

	The vertex $v_1$ belongs to $Tree(x_1,H_1)$
	for a unique $x_1\in Center(H_1)$. By the previous lemma there exist a vertex $v_2$ in 
	$Tree(f(x_1),H_2)$ such that the path $P(v_1)$, 
	joining $v_1$ and $x_1$, is isomorphic to the path
	$P(v_2)$, joining $v_2$ and $f(x_1)$, through an isomorphism $f^\prime: P(v_1)
	\rightarrow P(v_2)$ satisfying properties (1), (2) and (3). 
	Let 
	\[H^\prime_2:=Core(G_1(c_1,\dots, c_t,c_{t+1}[v_2]);r).\]
	We are going to show that $H^\prime_1\morph{k-1}H^\prime_2$.
	Clearly $Center(H^\prime_i)=Center(H_i)\cup P(v_1)$ for $i=1,2$ , so we can glue
	$f$ and $f^\prime$ into an isomorphism $g:Center(H^\prime_1)\rightarrow Center(H^\prime_2)$.
	Let $w_1\in H^\prime$. Then either
	\begin{itemize}
		\item $Tree(w_1,H_1)$ contains no edges in $P(v_1)$. 
		In this case $Tree(w_1,H^\prime_1)=Tree(w_1,H_1)$.
		Thus, $Tree(w_1,H^\prime_1)\morph{k} Tree(g(w_1),H^\prime_1)$
		and $Tree(w_1,H^\prime_1)\morph{k-1} Tree(g(w_1),H^\prime_1)$
		in consequence by lemma REF.
		\item $Tree(w_1,H_1)$ contains edges from $P(v_1)$.
		In this case, $Tree(w_1,H_1)$ contains exactly one initial edge
		$e_1$ in $P(v_1)$, and $Tree(w_1,H^\prime_1)=Tree(w_1,H_1)\setminus e_1$.
		One can check that $Tree(g(w_1),H_2)$ contains exactly one edge
		in $P(v_2)$, namely $g(e_1)$, and 
		$Tree(g(w_1),H^\prime_2)=Tree(g(w_1),H_2)\setminus g(e_1)$.
		We had $Tree(w_1,H_1)\morph{k}Tree(g(w_1),H_2)$, so by lemma REF
		$Tree(w_1,H^\prime_1)\morph{k-1}Tree($ $g(w_1),H^\prime_2)$.	
	\end{itemize}
\end{proof}

\begin{definition}
	Let $G_1,G_2$ be graphs with constants. We say that $G_1$ and $G_2$ are
	$k$-agreeable if for each $\morph{k}$ class $C$ of connected graphs either
	\begin{itemize}
		\item $G_1$ and $G_2$ have the same number of connected components of type $C$, or
		\item Both $G_1$ and $G_2$ have no less than $k$ connected components of type $C$.
	\end{itemize} 
\end{definition}

\begin{theorem} 
	Let $G_1, G_2$ be $k,3^k$-rich graphs such that $Core(G_1;3^k)$ is $k$-agreeable
	with $Core(G_2;3^k)$. Then Duplicator has a winning strategy in 
	the $E.F$ game on $G_1$ and $G_2$. 
\end{theorem}
\begin{proof}
	We will show, by induction on $i$, that Duplicator can play in such a way
	that in the $i$-th round $Core(G_1(c_1[x_1],\dots,c_i[x_i]);3^{k-i})$
	is $k-i$-agreeable with  $Core(G_2(c_1[y_1],\dots,c_i[y_i]);3^{k-i})$,
	where for each $j=1,\dots,i$,0 $x_j,y_j$ are the $j$-th 
	chosen vertex in the graphs $G_1$ and $G_2$	respectively. After this the theorem
	follows because
	$Core(G_1(c_1[x_1],\dots,c_i[x_k]);1)$ being $0$-agreeable with
	$Core(G_2(c_1[y_1],\dots,c_i[y_k]);1)$ implies that
	the map given by $x_i\mapsto y_i$ defines a partial isomorphism. \par
	\begin{itemize}[leftmargin=*]
		\item For $i=0$ the statement is true by hypothesis. 
		\item Assume now that $Core(G_1(c_1[x_1],\dots,c_i[x_{i-1}]);3^{k-i+1})$
		is $k-i+1$-agreeable with $Core(G_2(c_1[y_1],\dots, c_i[y_{i-1}]); 3^{k-i+1})$.
		Without loss of generality we can suppose that Spoiler chooses a vertex 
		$x_i$ in $G_1$ in the $i$-th round. We have two cases.
		\begin{itemize}[leftmargin=*]
			\item[Case 1.] $N(x_i;3^{k-i})$ is contained in 
			$Core(G_1(c_1[x_1],\dots,c_i[x_{i-1}]);3^{k-i+1})$.
			Let $H_1$ be the connected component of $Core(G_1(c_1[x_1],\dots,c_i[x_{i-1}]);3^{k-i+1})$
			containing $N(x_i;3^{k-i})$. Then there is a connected component $H_2$
			in $Core(G_2(c_1[y_1],\dots,$ $c_i[y_{i-1}]);3^{k-i+1})$ such that
			$H_1 \morph{k-i+1} H_2$. Applying theorems REF and REF successively Duplicator can choose
			$y_i\in V(H_2)$ such that 
			\[ Core(H_1(c_i[x_i]); 3^{k-1})\morph{k-i} Core(H_2(c_i[y_i]); 3^{k-1}).\]
			Using Theorem Ref and counting the connected components in each $k-i$-morphism class
			one can check that now $Core(G_1(c_1[x_1],\dots,c_i[x_i]);3^{k-i})$
			is $k-i$-agreeable with  $Core(G_2(c_1[y_1],\dots,c_i[y_i]);3^{k-i})$.
			\item[Case 2.] $N(x_i;3^{k-i})$ is contained in 
			$Core(G_1(c_1[x_1],\dots,c_i[x_{i-1}]);3^{k-i+1})$. Then
			$N(x_i;3^{k-i})$ is disjoint from $Core(G_1(c_1[x_1],\dots,c_i[x_{i-1}]);3^{k-i})$
			and in particular, $N(x_i;3^{k-i})$ is a tree. As $G_2$ was originally $k,3^k$-rich
			Duplicator can choose $y_i$ in $G_2$ such that $N(y_i;3^{k-i})$ is disjoint from 
			$Core(G_2(c_1[y_1],\dots,c_i[y_{i-1}]);3^{k-i})$ and the tree $N(x_i;3^{k-i})$
			rooted at $x_i$ is $k-i$-morphic to the tree $N(y_i;3^{k-i})$ rooted at $y_i$.
			Counting connected components of each type we can conclude that
			$Core(G_1(c_1[x_1],\dots,c_i[x_i]);3^{k-i})$
			is $k-i$-agreeable with  $Core(G_2(c_1[y_1],\dots,c_i[y_i]);3^{k-i})$.
		\end{itemize}  		
	\end{itemize}

\end{proof}
